Thesis outline

### 2017-06-12 KellyDouglass/Thesis/CV.tex
Updated Intro, Conclusion

\begin{itemize} %\itemsep -2pt
	\item ``Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$". \href{https://doi.org/10.3847/1538-4357/aa5e53}{ApJ, 837: 42--55}, 2017
	\item ``Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies". \href{https://doi.org/10.3847/1538-4357/834/2/186}{ApJ, 834: 186--198}, 2017
\end{itemize}

@@

\begin{itemize}[noitemsep]
	\item \textbf{Professor Bob's Hands-On Science} \hfill \textit{June 2015 to August 2016}
	\item \textbf{Volunteer at the Lynch Observatory} \hfill \textit{September 2011 to July 2017}
\end{itemize}

>>>>

\begin{itemize} %\itemsep -2pt
    \item Douglass, K.A., Vogeley, M.S., \& Cen, R.  ``Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass". \href{https://doi.org/}{submitted to ApJ}, 2017
	\item Douglass, K.A. \& Vogeley, M.S.  ``Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$". \href{https://doi.org/10.3847/1538-4357/aa5e53}{ApJ, 837: 42--55}, 2017
	\item Douglass, K.A. \& Vogeley, M.S.  ``Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies". \href{https://doi.org/10.3847/1538-4357/834/2/186}{ApJ, 834: 186--198}, 2017
\end{itemize}

@@

\begin{itemize}[noitemsep]
	\item \textbf{Professor Bob's Hands-On Science} \hfill \textit{June 2015 to July 2017}
	\item \textbf{Volunteer at the Lynch Observatory} \hfill \textit{September 2011 to June 2017}
\end{itemize}

### 2017-06-12 KellyDouglass/Thesis/DirectMethodPhysics.tex
Added simulations appendix section
Finished writing intro
Added intro figures
Updated Intro, Conclusion

\chapter{The physics of the Direct $T_e$ method}

UV photons from young stars in an \ion{H}{2} region keep the interstellar gas 
partially ionized.  In an \ion{H}{2} region, a photon with an energy 
$E_\gamma \gtrsim 13.6\text{ eV}$ ionizes a hydrogen atom, producing an H$^+$ 
ion and an electron with some kinetic energy 
$K_{e^-} = E_\gamma - 13.6\text{ eV}$.  As the free electron moves around in the 
gas, it loses some of its kinetic energy as it collisionally excites other ions 
in the gas.  Because we are in a Str\"{o}mgren sphere (an ionized region or an 
\ion{H}{2} region), the cross-section for this electron scattering is much 
larger than the photoionization cross section, so the free electrons will 
thermalize quickly \citep{DeRobertis87}.  Eventually, the free electron 
recombines with an H$^+$ ion, forming atomic hydrogen again.  The ions that were 
collisionally excited by the electron before its recombination eventually 
de-excite via forbidden transitions, emitting radiation that escapes the 
\ion{H}{2} region.

@@

\section{Temperatures from the forbidden emission lines}

@@

Expanding the description in Sec. \ref{sec:O3}, we can define the ratio of the 
emission line strengths for [\ion{O}{3}] $\lambda$4363 and [\ion{O}{3}] 
$\lambda \lambda$4959,5007 as
\begin{equation}
    \frac{j_{4959} + j_{5007}}{j_{4363}} = \frac{\Omega(^3\text{P}, ^1\text{D})}{\Omega(^3\text{P}, ^1\text{S})} \left[ \frac{A_{^1\text{S}, ^1\text{D}} + A_{^1\text{S}, ^3\text{P}}}{A_{^1\text{S}, ^1\text{D}}} \right] \frac{\bar{\nu}(^3\text{P}, ^1\text{D})}{\nu(^1\text{D}, ^1\text{S})} e^{\Delta E/kT}
\end{equation}
where $j_\lambda$ is the emissivity of the emission line, $\Omega (i,j)$ is the 
collision strength between levels $i$ and $j$, $A_{i,j}$ is the radiative 
transition probability between an upper level $i$ and a lower level $j$, $\nu$ 
is the frequency of the transition, $\Delta E$ is the energy difference between 
the $^1$D$_2$ and $^1$S$_0$ levels, and $T$ is the electron temperature 
\cite{Osterbrock89}.  The transition probabilities $A_{i,j}$ do not depend on 
the temperature, but the collision strength $\Omega (i,j)$ is 
temperature-dependent.  We can define
\begin{equation}
    \bar{\nu}(^3\text{P}, ^1\text{D}) = \frac{A_{^1\text{D}_2, ^3\text{P}_2} \nu (5007) + A_{^1\text{D}_2, ^3\text{P}_1} \nu (4959)}{A_{^1\text{D}_2, ^3\text{P}_2} + A_{^1\text{D}_2, ^3\text{P}_1}}
\end{equation}
Inserting numerical values for the collision strengths and transition 
probabilities from \cite{Osterbrock89}, the ratio becomes
\begin{equation}
    \frac{j_{4959} + j_{5007}}{j_{4363}} = \frac{7.73 \exp[(3.29\times 10^4)/T]}{1 + 4.5\times 10^{-4} (N_e/T^{1/2})}
\end{equation}
By measuring the flux of these emission lines, we can then solve for the 
temperature of the gas.

>>>>

\chapter[Direct method physics]{The physics of the Direct $T_e$ method}\label{sec:physics}

UV photons from young stars in an \ion{H}{2} region keep the interstellar gas 
partially ionized.  In an \ion{H}{2} region, a photon with an energy 
$E_\gamma \gtrsim 13.6\text{ eV}$ ionizes a hydrogen atom, producing an H$^+$ 
ion and an electron with some kinetic energy 
$K_{e^-} = E_\gamma - 13.6\text{ eV}$.  As the free electron moves around in the 
gas, it loses some of its kinetic energy as it collisionally excites other ions 
in the gas.  Because we are in a Str\"{o}mgren sphere (an ionized region or an 
\ion{H}{2} region), the cross-section for this electron scattering is much 
larger than the photoionization cross section, so the free electrons will 
thermalize quickly \citep{DeRobertis87}.  Eventually, the free electron 
recombines with an H$^+$ ion, forming atomic hydrogen.  The ions that are 
collisionally excited by the electron before its recombination eventually 
de-excite via forbidden transitions, emitting radiation that escapes the 
\ion{H}{2} region.

@@

%\section{Forbidden transitions}
%
%Similar to a fingerprint, every element has a unique set of wavelengths seen in 
%its spectrum that corresponds to the atom's different energy levels.  Since 
%electrons within an atom have discrete energy levels, transitions between levels 
%result in either the emission (when decreasing in energy) or absorption 
%(an increase in energy) of a photon of the same energy as the difference between 
%the two levels.  The separation between energy levels is unique for each 
%element, so the photon energies either emitted or absorbed by each element are 
%unique.
%
%
%\subsection{Time-dependent perturbation theory}
%
%A time-dependent potential is added to the Schr\"{o}dinger equation in order to 
%solve for the forbidden transition energies.  We can assume that the time 
%perturbation is a minor component of the potential and can thus treat it as a 
%perturbation.  For a simplified two-level system, the time-dependent wave 
%function is
%\begin{equation}
%    \Psi (t) = c_a (t) \psi_a e^{iE_a t/\hbar} + c_b (t) \psi (b) e^{-iE_b t/\hbar}
%\end{equation}
%To solve for the time-dependent coefficients, we substitute $\Psi (t)$ into the 
%time-dependent Schr\"{o}dinter equation
%\begin{equation}
%    H\Psi = i\hbar \frac{\partial \Psi}{\partial t}, \qquad \text{where} H = H^0 + H'(t)
%\end{equation}
%We find that
%\begin{align}
%    \dot{c}_a &= -\frac{i}{\hbar} H'_{ab} e^{-i\omega_0 t} c_b\\
%    \dot{c}_b &= -\frac{i}{\hbar} H'_{ba} e^{-i\omega_0 t} c_a
%\end{align}
%where
%\begin{equation}
%    \omega_0 \equiv \frac{E_b - E_a}{\hbar}
%\end{equation}
%and
%\begin{equation}
%    H_{ij} \equiv \langle \psi_i | H' | \psi_j \rangle
%\end{equation}
%The probability that transmission has occurred is $P_{b\to a} = |c_a (t)|^2$.  
%The transmission rate $R_{a\to b} = dP/dt$.
%
%For an electromagnetic wave, the atom experiences an oscillating electric field.  
%For visible light, it is safe to assume that the spatial portion of the field 
%does not change, since the wavelength is much longer than the size of the atom.  
%This oscillating field corresponds to our perturbing Hamiltonian:
%\begin{equation}
%    H' = -qE_0 z\cos (\omega t)
%\end{equation}
%where $q$ is the charge on the electron, and the electric field is oscillating 
%in the $z$ direction.  Thus,
%\begin{equation}
%    H'_{ba} = -pE_0 \cos (\omega t), \qquad \text{where} p \equiv q \langle \psi_b |z| \psi_a \rangle
%\end{equation}
%
%
%\subsection{Selection rules}
%
%The transmission rates depend on a matrix element of the form 
%$\langle \psi_b |\vec{r}| \psi_a \rangle$.  Denoting the states by the quantum 
%numbers $n$, $l$, and $m$, the matrix elements can be written as
%\begin{equation}
%    \langle n'l'm' |\vec{r}| nlm \rangle
%\end{equation}
%By applying the various angular momentum commutators \citep[as shown in][]
%{Griffiths05}, we can develop a set of selection rules for allowed transitions 
%of the electron in an atom.

\section[Estimating the temperature]{Temperatures from the forbidden emission lines}

@@

Expanding the description in Sec. \ref{sec:O3}, we can define the ratio of the 
emission line strengths for [\ion{O}{3}] $\lambda$4363 and [\ion{O}{3}] 
$\lambda \lambda$4959,5007 as
\begin{equation}
    \frac{j_{4959} + j_{5007}}{j_{4363}} = \frac{\Omega(^3\text{P}, ^1\text{D})}{\Omega(^3\text{P}, ^1\text{S})} \left[ \frac{A_{^1\text{S}, ^1\text{D}} + A_{^1\text{S}, ^3\text{P}}}{A_{^1\text{S}, ^1\text{D}}} \right] \frac{\bar{\nu}(^3\text{P}, ^1\text{D})}{\nu(^1\text{D}, ^1\text{S})} e^{\Delta E/kT}
\end{equation}
where $j_\lambda$ is the emissivity of the emission line, $\Omega (i,j)$ is the 
collision strength between levels $i$ and $j$, $A_{i,j}$ is the radiative 
transition probability between an upper level $i$ and a lower level $j$, $\nu$ 
is the frequency of the transition, $\Delta E$ is the energy difference between 
the $^1$D$_2$ and $^1$S$_0$ levels, and $T$ is the electron temperature 
\citep{Osterbrock89}.  The transition probabilities $A_{i,j}$ do not depend on 
the temperature, but the collision strength $\Omega (i,j)$ is 
temperature-dependent.  We can define
\begin{equation}
    \bar{\nu}(^3\text{P}, ^1\text{D}) = \frac{A_{^1\text{D}_2, ^3\text{P}_2} \nu (5007) + A_{^1\text{D}_2, ^3\text{P}_1} \nu (4959)}{A_{^1\text{D}_2, ^3\text{P}_2} + A_{^1\text{D}_2, ^3\text{P}_1}}
\end{equation}
Inserting numerical values for the collision strengths and transition 
probabilities from \cite{Osterbrock89}, the ratio becomes
\begin{equation}
    \frac{j_{4959} + j_{5007}}{j_{4363}} = \frac{7.73 \exp[(3.29\times 10^4)/T]}{1 + 4.5\times 10^{-4} (N_e/T^{1/2})}
\end{equation}
By measuring the flux of these emission lines, we can then solve for the 
temperature of the gas.

### 2017-06-12 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Updated Intro, Conclusion

% Papers 1-3
\section[Chemical abundances]{Large-scale environmental influence on the gas-phase chemical abundances in dwarf galaxies}
We find that the large-scale environment influences the chemical evolution of 
dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
in the MPA-JHU catalog \citep[Douglass \& Vogeley 2017, in prep]{Douglass17a,
Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
$\lambda$3727 emission line in SDSS DR7 spectra, only 135 dwarf galaxies are 
available for analysis with the Direct $T_e$ method.  With this sample, we 
initially see no difference in the metallicity (O/H) between dwarf galaxies in 
voids and in denser regions.  However, upon closer inspection, we find minor 
shifts in the distributions of gas-phase chemical abundances for void dwarf 
galaxies when compared to star-forming dwarf galaxies in denser regions: 
star-forming dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
abundances (N/H), and lower N/O ratios.

By deriving a relation between the doubly-ionized oxygen and total oxygen 
abundance in star-forming galaxies, we can expand our sample to consist of 1920 
star-forming galaxies by removing the dependence on the [\ion{O}{2}] 
$\lambda$3727 doublet.  This larger sample exhibits the same shifts in the 
gas-phase chemical abundances as the smaller, 135 star-forming dwarf galaxy 
sample, but with a much higher statistical significance.  We find that 
star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances, 
10\% lower nitrogen abundances, and 17\% lower N/O ratios than star-forming 
dwarf galaxies in denser regions.  The large-scale ($\sim 10$ \hMpc) environment 
influences the chemical evolution of star-forming dwarf galaxies.

In addition to studying the large-scale environmental influence on the 
distribution of gas-phase chemical abundances in star-forming dwarf galaxies, we 
also investigate if and how the large-scale environment affects relationships 
between the chemical abundances and various other physical parameters of the 
galaxies.  We find that all of our galaxies reside on the ``nitrogen plateau'' 
in the relationship between N/O and O/H, where the N/O ratio is predicted to be 
independent of metallicities \OH $< 8.5$.  However, instead of a constant value 
for the N/O ratio, we instead find that the N/O ratio decreases with increasing 
metallicity.  This is contrary to what we see in the N/O-$M_*$ relationship, 
where we find that some of the star-forming dwarf galaxies have a constant value 
of N/O for a range of masses while the remainder exhibit a positive relationship 
between the stellar mass and N/O ratio.  We make note of a different critical 
mass in the N/O-$M_*$ relationship in the two environments, where the void dwarf 
galaxies begin to show evidence of secondary nitrogen synthesis at a stellar 
mass $\sim 0.4\text{ dex}$ lower than for the galaxies in denser regions.  Most 
of our star-forming dwarf galaxies follow the established mass-metallicity 
relation \citep[e.g.,][]{Tremonti04}.

No relationship is observed between the metallicity and \ion{H}{1} mass in our 
sample of star-forming dwarf galaxies, but we do find that the N/O ratio 
decreases with increasing \ion{H}{1} mass for a given stellar mass.  The 
star-forming dwarf galaxies also exhibit an increase in the metallicity and 
N/O ratio with increasing color (both $u-r$ and $g-r$).  We see very little 
correlation with SFR for either metallicity or the N/O ratio in dwarf galaxies, 
but the metallicity and N/O ratio decrease with increasing sSFR.  Beyond the 
large-scale environmental influence on the distributions of the gas-phase 
chemical abundances and the critical mass in the N/O-$M_*$ relationship, we do 
not observe any significant differences between the star-forming void and wall 
dwarf galaxies in any of these relationships.

We surmise that the differences in the distributions of metallicity and the N/O 
ratio seen in the sample of star-forming dwarf galaxies are due to a large-scale 
environmental influence on their star formation history and evolution.  The 
shift in the gas-phase oxygen abundance distribution could be observational 
evidence for delayed star formation in void galaxies when compared to those in 
denser regions.  This would result in a smaller ratio of stellar mass to dark 
matter halo mass in void galaxies than in dwarf galaxies in denser regions, as 
predicted in simulations by \cite{Jung14} and \cite{Tonnesen15}.  If the void 
galaxies are retaining more oxygen as a result of their deeper potential wells, 
then they would be able to commence secondary nitrogen synthesis earlier, as 
seen in the N/O-$M_*$ relation in Fig. \ref{fig:M_NO}.  In addition, the shift 
towards lower N/O ratios in the star-forming dwarf galaxies might be evidence 
that cosmological downsizing is environmentally dependent as predicted by 
\cite{Cen11}.  Our results provide evidence for delayed, ongoing star formation 
in void dwarf galaxies whose dark matter halos ceased coalescing earlier than 
for dwarf galaxies in denser regions.

@@

% Small-scale environment
\section[Small-scale environment]{Small-scale environmental influence on dwarf galaxy evolution}
In addition to the influence of the large-scale environment on the evolution of 
dwarf galaxies, we also study the effects of the small-scale environment on dwarf 
galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
\hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
0.05 \hMpc or 0.05$r_{vir}$ are bluer, have a higher sSFR, and have higher 
oxygen and nitrogen abundances than average.  In contrast, dwarf galaxies within 
0.1 \hMpc of the center of the closest group are redder, have lower oxygen 
abundances, and have higher N/O ratios than average.  These results are 
independent of the maximum relative velocity required to define a nearest 
neighbor and the sample (star-forming versus all dwarf galaxies).

When we incorporate the redshift into the distance calculations, we find that 
the galaxies within 0.05$r_{vir}$ are most likely strongly interacting or 
merging with their nearest neighbor.  This matches the results of \cite{Park09}, 
who find that late-late type galaxy pairs within 0.05$r_{vir}$ are bluer and 
have higher SFRs.  These merging galaxies likely share the same dark matter 
halo, indicating that the dark matter halo is more influential on a galaxy's 
evolution than the galaxy's distance to the nearest neighbor.

% GV galaxies
\section[GV galaxies]{Properties of green valley galaxies}
Finally, we also investigate the properties of galaxies residing in the green 
valley of the color-magnitude diagram (CMD), in an effort to understand the role 
of the environment on a galaxy's evolution through the color-magnitude diagram.  
We discover that we can define galaxies which are transitioning through the 
green valley of the CMD by combining the galaxy's color, color gradient, and 
inverse concentration index.  Galaxies with a magnitude less than 25 for the 
morphological type as calculated in the KIAS-VAGC exist in the green valley 
portion of the UV-optical CMD.  Galaxies defined as early types (morphological 
type values equal to 1 or 2) are in the red cloud, while those with 
morphological type values greater than 25 are in the blue sequence.  With this 
quantitative definition for galaxies transitioning through the green valley, we 
can begin to understand the properties of green valley galaxies and their 
evolution.

@@

A better knowledge of the chemical abundances of galaxies with an AGN is also 
crucial to understanding the evolution of galaxies.  Understanding how the 
presence of an AGN affects a galaxy's evolution is currently limited --- most 
research at the moment is concentrated on the physics within an AGN.  Many 
simulations have been done to test different theories about the role of an AGN 
in a galaxy, and observations are now needed to test the results of the 
simulations.

>>>>

% Papers 1-3
\section[Chemical abundances]{Large-scale environmental influence on the gas-phase chemical abundances in dwarf galaxies}
We find that the large-scale environment influences the chemical evolution of 
dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
in the MPA-JHU catalog \citep[Douglass et al., 2017, in prep]{Douglass17a,
Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
$\lambda$3727 emission line in SDSS DR7 spectra, only 135 star-forming dwarf 
galaxies are available for analysis with the Direct $T_e$ method.  With this 
sample, we see no difference in the metallicity (O/H) between dwarf galaxies in 
voids and denser regions \citep{Douglass17a}.  Upon closer inspection, we find 
minor shifts in the distributions of gas-phase chemical abundances for void 
dwarf galaxies when compared to dwarf galaxies in denser regions: star-forming 
void dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
abundances (N/H), and lower N/O ratios \citep{Douglass17b}.

By deriving a relation between the doubly-ionized oxygen and total oxygen 
abundance in star-forming galaxies, we can expand our sample to consist of 1920 
star-forming dwarf galaxies by removing the dependence on the [\ion{O}{2}] 
$\lambda$3727 doublet.  This larger sample exhibits the same shifts in the 
gas-phase chemical abundances as the smaller, 135 star-forming dwarf galaxy 
sample, but with a much higher statistical significance.  We find that 
star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances, 
10\% lower nitrogen abundances, and 17\% lower N/O ratios than star-forming 
dwarf galaxies in denser regions.  The large-scale ($\sim 10$ \hMpc) environment 
influences the chemical evolution of star-forming dwarf galaxies.

In addition to studying the large-scale environmental influence on the 
distribution of gas-phase chemical abundances in star-forming dwarf galaxies, we 
also investigate if and how the large-scale environment affects relationships 
between the chemical abundances and various other physical properties of the 
galaxies.  We find that the N/O ratio decreases with increasing metallicity 
rather than a constant value for the N/O ratio as a function of O/H as observed 
in other studies.  This is contrary to what we see in the $M_*$-N/O 
relationship, where we find that some of the star-forming dwarf galaxies have a 
constant value of N/O for a range of masses while the remainder exhibit a 
positive relationship between the stellar mass and N/O ratio.  We make note of a 
different critical mass in the $M_*$-N/O relationship in the two environments, 
where the void dwarf galaxies begin to show evidence of secondary nitrogen 
synthesis at a stellar mass $\sim$0.4 dex lower than for the galaxies in denser 
regions.  Most of our star-forming dwarf galaxies follow the established 
mass-metallicity relation \citep[e.g.,][]{Tremonti04}.

No relationship is observed between the metallicity and \ion{H}{1} mass in our 
sample of star-forming dwarf galaxies, but we find that the N/O ratio decreases 
with increasing \ion{H}{1} mass for a given stellar mass.  The star-forming 
dwarf galaxies also exhibit an increase in the metallicity and N/O ratio with 
increasing color (both $u-r$ and $g-r$).  We see very little correlation with 
SFR for either metallicity or the N/O ratio in dwarf galaxies, but the 
metallicity and N/O ratio decrease with increasing sSFR.  Beyond the large-scale 
environmental influence on the distributions of the gas-phase chemical 
abundances and the critical mass in the $M_*$-N/O relationship, we do not 
observe any significant differences between the star-forming void and wall dwarf 
galaxies in any of these relationships.

We surmise that the differences in the distributions of metallicity and the N/O 
ratio seen in the sample of star-forming dwarf galaxies are due to a large-scale 
environmental influence on their star formation history and evolution.  The 
shift in the gas-phase oxygen abundance distribution could be observational 
evidence for delayed star formation in void galaxies when compared to those in 
denser regions.  This would result in a smaller ratio of stellar mass to dark 
matter halo mass in void galaxies than in dwarf galaxies in denser regions, as 
predicted in simulations by \cite{Jung14} and \cite{Tonnesen15}.  If the void 
galaxies are retaining more oxygen as a result of their deeper potential wells, 
then they would be able to commence secondary nitrogen synthesis earlier, as 
seen in the $M_*$-N/O relation in Fig. \ref{fig:M_NO}.  In addition, the shift 
towards lower N/O ratios in the star-forming dwarf galaxies might be evidence 
that cosmological downsizing is environmentally dependent as predicted by 
\cite{Cen11}.  Our results provide evidence for delayed, ongoing star formation 
in void dwarf galaxies whose dark matter halos ceased coalescing earlier than 
for dwarf galaxies in denser regions.

@@

% Small-scale environment
\section[Small-scale environment]{Small-scale environmental influence on dwarf galaxy evolution}
In addition to the influence of the large-scale environment on the evolution of 
dwarf galaxies, we also study the effects of the small-scale environment on dwarf 
galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
\hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
0.05 \hMpc or 0.05$r_{vir}$ are bluer, have a higher sSFR, and have higher 
oxygen and nitrogen abundances than average.  This matches the results of 
\cite{Park09}, who find that late-late type galaxy pairs within 0.05$r_{vir}$ 
are bluer and have higher SFRs.  In contrast, dwarf galaxies within 0.1 \hMpc of 
the center of the closest group are redder, have lower oxygen abundances, and 
have higher N/O ratios than average.  These results are independent of both the 
maximum relative velocity required to define a nearest neighbor and the sample 
(star-forming versus all dwarf galaxies).

When we incorporate the redshift into the distance calculations, we find that 
the galaxies within 0.05$r_{vir}$ are most likely strongly interacting or 
merging with their nearest neighbor.  These merging galaxies likely share the 
same dark matter halo, suggesting that the dark matter halo is more influential 
on a galaxy's evolution than the distance between a galaxy and its nearest 
neighbor.

% GV galaxies
\section[GV galaxies]{Properties of green valley galaxies}
Finally, we also investigate the properties of galaxies residing in the green 
valley of the color-magnitude diagram (CMD) in an effort to understand the role 
of the environment on a galaxy's evolution through the color-magnitude diagram.  
We discover that we can define galaxies which are transitioning through the 
green valley of the CMD by combining the galaxy's color, color gradient, and 
inverse concentration index.  Galaxies with a value less than 25 for the 
morphological type as calculated in the KIAS-VAGC exist in the green valley 
portion of the UV-optical CMD.  Galaxies defined as early types (morphological 
type values equal to 1 or 2) are in the red cloud, while those with 
morphological type values greater than 25 are in the blue sequence.  With this 
quantitative definition for galaxies transitioning through the green valley, we 
can begin to understand the properties of green valley galaxies and their 
evolution.

@@

A better knowledge of the chemical abundances of galaxies with an AGN is also 
crucial to understanding the evolution of galaxies.  Understanding how the 
presence of an AGN affects a galaxy's evolution is currently limited --- at the 
moment, most research is concentrated on the physics within an AGN.  Many 
simulations have been done to test different theories about the role of an AGN 
in a galaxy, and observations are now needed to test the results of the 
simulations.
